Mathematical Gene Network Evolution

### 2017-01-31 kalman_walk.tex
added more references and changed the title.
a few more things to the future list

@@

Epistasis, coming from mutations deleterious in some networks but not in others
(come from incompatibilities).

Describe heterosis.

Distribution of dominance coefficients.

>>>>

    \item Figure out coherent model for changing dimension: do coefficients stay stuck at zero? In what parameterization? 
        Do we need to allow deleterious variation to get deletion?

@@

\begin{enumerate}

    \item Epistasis, coming from mutations deleterious in some networks but not in others
(come from incompatibilities).

    \item Describe heterosis.

    \item Distribution of dominance coefficients.

    \item Evolvability: easier for bigger networks to adapt to a new environment?

    \item Do short-term responses to strong directional selection have deleterious epistatic consequences in other traits?
